---
title: "README"
output: md_document
---

https://www.kaggle.com/c/g2net-gravitational-wave-detection/overview

Nice book about sound analysis using R [](https://link.springer.com/book/10.1007/978-3-319-77647-7), it shows many examples for plotting spectorgrams

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Read file npy

```{r gravitational waves}
library(RcppCNPy)
library(tidyverse)
library(tuneR)
library(seewave)

"00000e74ad.npy" %>% npyLoad() -> imat

imat %>%
  t() %>%
  as.data.frame() %>%
  rename( x =V1 , y = V2 , z = V3) %>%
  add_column( index = 1:(imat %>% ncol()) ) %>%
  gather( key, value , -index ) %>%
  ggplot( aes (y = value, x = index) ) +
  geom_line() +
  facet_grid(rows = vars(key)) +
  xlab("Time") + ylab("Intensity")


```



```{r  Frequency Anlysis}

readWaveFromNpy <- function(filePath,index) {
  filePath %>%
          npyLoad() %>%
          .[index,] %>%
          scale()  %>%
          Wave( left = .,samp.rate = 2048 )

}

"00001f4945.npy" %>% readWaveFromNpy(1)  %>% spec( flim = c(0,0.05) )


```





## Including Plots

You can also embed plots, for example:

```{r}

"00001f4945.npy" %>% npyLoad() %>% scale()-> imat
imat <- imat * 20
imat %>%  .[2,] %>% Wave( left = .,samp.rate = 2048 )  %>%
  spectro( flim = c(0,0.2) , palette = colorRampPalette(c("white", "blue", "green")) , ovlp = 50)

```

similar to [example](https://rug.mnhn.fr/seewave/spec.html)
the code was copied form the above source, we have refactored it into different functions, to avoid occyping the memory with temporarly useless data
the result we are looking is to plot some graphs.

```{r}
library(RcppCNPy)
library(tidyverse)
library(seewave)
library(tuneR)
library(ggplot2)
library(viridis)
library(grid)
library(gridExtra)


# x label formatter
s_formatter <- function(x){
  lab <- paste0(x, " s")
}

# y label formatter
khz_formatter <- function(y){
  lab <- paste0(y, " kHz")
}



buildDataFrameOfWave <- function(wav) {
  sample <- seq(1:length(wav@left))
  time <- sample/wav@samp.rate
  sample.left <- wav@left %>% cbind() %>% as.vector()
  sample %>% data.frame( time, sample.left)
}


buildSpectrograph <- function(wav) {
  hot_colors <- inferno(n=20)

  hot_theme_grid <- theme(panel.grid.major.y = element_line(color="black", linetype = "dotted"),
                          panel.grid.major.x = element_blank(),
                          panel.grid.minor = element_blank(),
                          panel.background = element_rect(fill="transparent"),
                          panel.border = element_rect(linetype = "solid", fill = NA, color = "grey"),

                          axis.line = element_blank(),

                          legend.position = "top",
                          legend.justification = "right",
                          legend.background = element_rect(fill="black"),
                          legend.key.width = unit(50, "native"),
                          legend.title = element_text(size=16, color="grey"),
                          legend.text = element_text(size=16, color="grey"),

                          plot.background = element_rect(fill="black"),
                          plot.margin = margin(1,1,0,1, "lines"),

                          axis.title = element_blank(),
                          axis.text = element_text(size=16, color = "grey"),
                          axis.text.x = element_blank(),
                          axis.ticks = element_line(color="grey"))

  wav %>%
          ggspectro( ovlp=90, flim=c(0,0.06))+
          scale_x_continuous(labels=s_formatter, expand = c(0,0))+
          scale_y_continuous(breaks = seq(from = 5, to = 20, by=5), expand = c(0,0), labels = khz_formatter, position = "right")+
          geom_raster(aes(fill=amplitude), hjust = 0, vjust = 0, interpolate = F)+
          scale_fill_gradientn(colours = hot_colors, name = "Amplitude \n (dB)", na.value = "transparent", limits = c(-60,0))+
          hot_theme_grid

}

buildOscilograph <- function(df) {
  oscillo_theme_dark <- theme(panel.grid.major.y = element_line(color="black", linetype = "dotted"),
                              panel.grid.major.x = element_blank(),
                              panel.grid.minor = element_blank(),
                              panel.background = element_rect(fill="transparent"),
                              panel.border = element_rect(linetype = "solid", fill = NA, color = "grey"),
                              axis.line = element_blank(),
                              legend.position = "none",
                              plot.background = element_rect(fill="black"),
                              plot.margin = unit(c(0,1,1,1), "lines"),
                              axis.title = element_blank(),
                              axis.text = element_text(size=14, color = "grey"),
                              axis.ticks = element_line(color="grey"))
    df %>%
          ggplot() +
          geom_line(mapping = aes(x=time, y=sample.left), color="grey")+
          scale_x_continuous(labels=s_formatter, expand = c(0,0))+
          scale_y_continuous(expand = c(0,0), position = "right")+
          geom_hline(yintercept = 0, color="white", linetype = "dotted")+
          oscillo_theme_dark
}


#-------------------------------------------
## PLOT GRID
#-------------------------------------------

showPlotsInGrid <- function( hotplot , oscplot ) {
  gA <- hotplot %>% ggplot_build() %>% ggplot_gtable()
  gB <- oscplot %>% ggplot_build() %>% ggplot_gtable()

  maxWidth = grid::unit.pmax(gA$widths, gB$widths)

  gA$widths <- as.list(maxWidth)
  gB$widths <- as.list(maxWidth)

  layo <- rbind(c(1,1,1),
                c(1,1,1),
                c(1,1,1),
                c(2,2,2))

  grid.newpage()
  grid.arrange(gA, gB, layout_matrix = layo)
}


showPlots <- function(wav) {
   hotplot = wav %>% buildSpectrograph()
   oscplot = wav %>% buildDataFrameOfWave() %>% buildOscilograph()
  showPlotsInGrid( hotplot, oscplot)
}

"00001f4945.npy" %>% readWaveFromNpy(2) %>% showPlots()




```





